### 2015-04-07 Kokkos_PG_LegacyCodeIntegration.tex
More updates to LegacyCodeIntegration

@@

\subsection{Keeping track of data transfers}

>>>>

\begin{lstlisting}
// Create a vector of 1000 double elements
Kokkos::vector<double> v(1000);
// Create another vector as a copy of v; This allocates another 1000 doubles
Kokkos::vector<double> x = v;

parallel_for(1000, KOKKOS_LAMBDA (const int& i) {
   // Create a view of x; m and x will reference the same data.
   Kokkos::vector<double> m = x; 
   x[i] = 2*i+1;
   v[i] = m[i] - 1;
});

// Now x contains the first 1000 uneven numbers
// v contains the first 1000 even numbers
\end{lstlisting}

@@

There are no restrictions on calling non-Kokkos libraries outside of parallel kernels. 
However due to the polymorphic layouts of Kokkos views it is often required to test
layouts for compatibility with third party libraries. The usual Blas interface for example,
expects matrixes to be laid out in column major format (i.e. LayoutLeft in Kokkos). 
Furthermore it is necessary to test that the library can access the memory space 
of the view.

\begin{lstlisting}
template<class Scalar, class DeviceType>
Scalar dot(View<const Scalar* , DeviceType> a, View<const Scalar*, DeviceType> b) {
// Check for Cuda memory and call cublas if true
#ifdef KOKKOS_HAVE_CUDA
  if(Impl::is_same<typename DeviceType::memory_space,CudaSpace> ::value ||
     Impl::is_same<typename DeviceType::memory_space,CudaUVMSpace> ::value) {
    return call_cublas_dot(a.ptr_on_device(),b.ptr_on_device(),a.dimension_0() );
  }
#endif

// Call CBlas on the host otherwise
  if(Impl::is_same<typename DeviceType::memory_space,HostSpace> ::value) {
    return call_cblas_dot(a.ptr_on_device(),b.ptr_on_device(),a.dimension_0() );
  }
}
\end{lstlisting}

Note the \lstinline|Impl::is_same| construct can be replaced
